### 2020-08-05 ART_Krzanowski/Krzanowski-PU.tex
P. Polak correctons added

\section{The problem of information}
\enlargethispage{\baselineskip}
This paper considers whether information should be understood as epistemic or ontological content or whether we need both concepts to fully account for the nature of information. While this paper suggests possible answers to the question and indicates some of the consequences for a particular choice, its objective is to demonstrate that both views can be argued for and that both perspectives have found recognition in scientific literature.

@@

In this view point, information as a concept is centered on a human or other conscious agent.\footnote{The term ``a conscious agent'' may, in addition to human agents, include animals or artificial systems.} We call this epistemic information, emphasizing its relation to knowledge and meaning, and denote it as information\textsubscript{E} or I\textsubscript{E}. Having this kind of information in mind, Norbert Weiner states, ``Information is a name for the content of what is exchanged with the outer world as we adjust to it, and make our adjustment felt upon it''

@@

 Loose 

@@

 or Carrol 

@@

\begin{small}
%\renewcommand*{\arraystretch}{1.4}
\begin{longtable}{p{.2\textwidth}p{.2\textwidth}p{.5\textwidth}}
{\bfseries Category of a model} &
{\bfseries Author} &
{\bfseries Main claim}\\
Human Cognitive agent &
Paul Beyond-Davis
%\label{ref:RNDGlvlgOHxMh}(2009)
\parencite*[][]{beynon-davies_business_2009}%

Luciano Floridi
%\label{ref:RNDVODwhFTa6P}(2010b)
\parencite*[][]{floridi_philosophy_2010}%
 &
Information is data + meaning.\\
&
Gregory Bateson
%\label{ref:RNDk3Ij9qZiMx}(1979)
\parencite*[][]{bateson_mind_1979}%
 &
Information consists of differences that make a difference.\\
&
Fred Dretske
%\label{ref:RNDBbigyfPfxw}(1999)
\parencite*[][]{dretske_knowledge_1999}%
 &
Information is sharply distinguished from meaning, at least for the concept of meaning relevant to semantic studies.\\
&
Buckland
%\label{ref:RNDveMzPg3oVF}(1991)
\parencite*[][]{buckland_information_1991}%
 &
Information-as-thing, information-as-knowledge, information-as-process\\
&
Ratzan
%\label{ref:RNDIw8xPlCabx}(2004)
\parencite*[][]{ratzan_understanding_2004}%
 &
Information is meaning\\
&
Davenport
%\label{ref:RND1P7GuBJBc6}(1997)
\parencite*[][]{davenport_information_1997}%
 &
Information is ``data endowed with relevance and purpose.''\\
Biological Agent &
John Maynard Smith
%\label{ref:RNDfoMBqK8sBS}(2000)
\parencite*[][]{maynard_smith_concept_2000}%
 &
DNA transmission is equivalent to a human communication channel.\\
Artificial cognitive agent &
David Vernon
%\label{ref:RND35RDE48snR}(2014)
\parencite*[][]{vernon_artificial_2014}%
 &
Information is what an artificial cognitive system extracts from its environment.\\
Formal models

@@

\section{Information: The ontological view}
From an alternative viewpoint for information, we see information as a form or organization of nature. We do not ask, ``What is information?'' in the context of a specific domain, cognitive agent, or communication process. Instead, we conceive information as an objective, mind-independent phenomenon. We see it as something that is a part of the natural world, and people are not reference points for it. We call such a thing ontological information and denote it by information\textsubscript{O} or I\textsubscript{O}. Conceptualizing information as an ontological phenomenon is less understood and researched, yet as we will see, it is well justified.

@@

For the sake of completeness, we may attempt to provide the definition of ontological information, however, as a fundamental concept, ontological information may be eluding the precise explication (as energy or matter do, see e.g. Keith Devlin above). Stonier defines ontological information as ``the capacity to organize a system or to maintain it in an organized state''. Carroll refers to ontological information as ``a complete specification of the exact state of a physical system''. Heller states that ``the word […] is a structure. This structure contains encoded information or is information''
%\label{ref:RNDXIMWnDGccm}(Heller, 1995, p.170).
\parencite[][p.170]{heller_nauka_1995}. %
 More complex and formal definitions such as Turek's require the specification of the whole framework of concepts (form, set, structure, substance, etc.) so they are omitted here 
%\label{ref:RNDhOdN9Z2Cew}(see e.g. Turek, 1978).
\parencite[see e.g.][]{turek_filozoficzne_1978}. %
 We may also mention Rovelli's 
%\label{ref:RNDOo0mgw7Idr}(2016)
\parencite*[][]{rovelli_meaning_2016} %
 definition of ``a purely physical version of the notion of information.'' Rovelli defines information (relative) as a correlation between states of physical systems, which is in his own words ``downright crude physical correlation'' 
%\label{ref:RNDqmJNxzsIuW}(Rovelli, 2016, p.1).
\parencite[][p.1]{rovelli_meaning_2016}. %
 The fact that his definition (derived from Shannon's information entropy) is applied to physical phenomena does not make it the definition of ontological information. Rovelli still looks for some form of meaning in physical structures (he calls it correlation), as he says ``purely physical definition of meaningful information.'' Ontological information, in the sense used in this paper, exists whether there is any correlation or not; it is the form of nature in a specific sense; nature as such has no meaning. Rovelli's concept of information seems to be just another mathematical representation of a certain perspective on nature's organization with rather overextended concept of meaning. The seat of meaning is a conscious agent, not physical structures, even if the ultimate nature of consciousness is biological.

@@

In a sense, both types of information exist, ontological as something concrete and epistemic as an abstract view of knowledge. From this perspective, ontological information acts as the carrier of what can potentially become epistemic information. Indeed, it is its main source, with the cognitive faculties of the mind itself being another source. I\textsubscript{e }is contingent, dependent, and relative because it is located in the mind. I\textsubscript{o}, meanwhile, is objective and meaningless, because it exists as a physical fact. We may need I\textsubscript{o} to get I\textsubscript{e}, but I\textsubscript{e} acquires its own ``persistence'' once created. While there is an obvious bottom-up causation from I\textsubscript{o }to I\textsubscript{e}, there is also a top-down causation from I\textsubscript{e }to I\textsubscript{o}. This means that in many cases, the forms and organization in physical reality (e.g., manmade objects) are expressions of mental concepts (I\textsubscript{e}). We may therefore imply an emergence relation between the two forms of information. However, this emergence must be properly understood. I\textsubscript{e} emerges from I\textsubscript{o} as a non-reducible ``entity.'' I\textsubscript{e} cannot be explained purely in terms of I\textsubscript{o}, because it acquires features that do not exist at the I\textsubscript{o} level. Another interpretation would involve regarding I\textsubscript{o }as representing the level of physical reality, which is in itself a multi-level reality with complex structures at different levels of organization for nature. In fact, we have multiple levels of I\textsubscript{o }to reflect nature's complexity. I\textsubscript{e}, meanwhile, represents the reality at the level of a living conscious agent. This reflects I\textsubscript{o}, but the agent creates its own specific representation. Which particular interpretation of I\textsubscript{o} and I\textsubscript{e} is most accurate should be the subject of future research.

>>>>

\section{The problem of information}
\enlargethispage{\baselineskip}
\lettrine[loversize=0.13,lines=2,lraise=-0.05,nindent=0em,findent=0.2pt]%
{T}{}his paper considers whether information should be understood as epistemic or ontological content or whether we need both concepts to fully account for the nature of information. While this paper suggests possible answers to the question and indicates some of the consequences for a particular choice, its objective is to demonstrate that both views can be argued for and that both perspectives have found recognition in scientific literature.

@@

In this view point, information as a concept is centered on a human or other conscious agent.\footnote{The term ``a conscious agent'' may, in addition to human agents, include animals or artificial systems.} We call this epistemic information, emphasizing its relation to knowledge and meaning, and denote it as information\textsubscript{e} or I\textsubscript{e}. Having this kind of information in mind, Norbert Weiner states, ``Information is a name for the content of what is exchanged with the outer world as we adjust to it, and make our adjustment felt upon it''

@@

 Losee 

@@

 or Caroll 

@@

\begin{small}
%\renewcommand*{\arraystretch}{1.4}
\begin{longtable}{p{.2\textwidth}p{.2\textwidth}p{.5\textwidth}}
{\bfseries Category of a model} &
{\bfseries Author} &
{\bfseries Main claim}\\
Human Cognitive agent &
Paul Beynon-Davis
%\label{ref:RNDGlvlgOHxMh}(2009)
\parencite*[][]{beynon-davies_business_2009}%

Luciano Floridi
%\label{ref:RNDVODwhFTa6P}(2010b)
\parencite*[][]{floridi_philosophy_2010}%
 &
Information is data + meaning.\\
&
Gregory Bateson
%\label{ref:RNDk3Ij9qZiMx}(1979)
\parencite*[][]{bateson_mind_1979}%
 &
Information consists of differences that make a difference.\\
&
Fred Dretske
%\label{ref:RNDBbigyfPfxw}(1999)
\parencite*[][]{dretske_knowledge_1999}%
 &
Information is sharply distinguished from meaning, at least for the concept of meaning relevant to semantic studies.\\
&
Michael Buckland
%\label{ref:RNDveMzPg3oVF}(1991)
\parencite*[][]{buckland_information_1991}%
 &
Information-as-thing, information-as-knowledge, information-as-process\\
&
Lee Ratzan
%\label{ref:RNDIw8xPlCabx}(2004)
\parencite*[][]{ratzan_understanding_2004}%
 &
Information is meaning\\
&
Thomas Davenport
%\label{ref:RND1P7GuBJBc6}(1997)
\parencite*[][]{davenport_information_1997}%
 &
Information is ``data endowed with relevance and purpose.''\\
Biological Agent &
John Maynard Smith
%\label{ref:RNDfoMBqK8sBS}(2000)
\parencite*[][]{maynard_smith_concept_2000}%
 &
DNA transmission is equivalent to a human communication channel.\\
Artificial cognitive agent &
David Vernon
%\label{ref:RND35RDE48snR}(2014)
\parencite*[][]{vernon_artificial_2014}%
 &
Information is what an artificial cognitive system extracts from its environment.\\
Formal models

@@

\section{Information: The ontological view}
From an alternative viewpoint for information, we see information as a form or organization of nature. We do not ask, ``What is information?'' in the context of a specific domain, cognitive agent, or communication process. Instead, we conceive information as an objective, mind-independent phenomenon. We see it as something that is a part of the natural world, and people are not reference points for it. We call such a thing ontological information and denote it by information\textsubscript{o} or I\textsubscript{o}. Conceptualizing information as an ontological phenomenon is less understood and researched, yet as we will see, it is well justified.

@@

For the sake of completeness, we may attempt to provide the definition of ontological information, however, as a fundamental concept, ontological information may be eluding the precise explication (as energy or matter do, see e.g. Keith Devlin above). Stonier defines ontological information as ``the capacity to organize a system or to maintain it in an organized state''. Carroll refers to ontological information as ``a complete specification of the exact state of a physical system''. Heller states that ``the word […] is a structure. This structure contains encoded information or is information''
%\label{ref:RNDXIMWnDGccm}(Heller, 1995, p.170).
\parencite[][p.170]{heller_nauka_1995}. %
 More complex and formal definitions such as Turek's require the specification of the whole framework of concepts (form, set, structure, substance, etc.) so they are omitted here 
%\label{ref:RNDhOdN9Z2Cew}(see e.g. Turek, 1978).
\parencites[see e.g.][]{turek_filozoficzne_1978}[see also][]{krzanowski_towards_2016}. %
 We may also mention Rovelli's 
%\label{ref:RNDOo0mgw7Idr}(2016)
\parencite*[][]{rovelli_meaning_2016} %
 definition of ``a purely physical version of the notion of information.'' Rovelli defines information (relative) as a correlation between states of physical systems, which is in his own words ``downright crude physical correlation'' 
%\label{ref:RNDqmJNxzsIuW}(Rovelli, 2016, p.1).
\parencite[][p.1]{rovelli_meaning_2016}. %
 The fact that his definition (derived from Shannon's information entropy) is applied to physical phenomena does not make it the definition of ontological information. Rovelli still looks for some form of meaning in physical structures (he calls it correlation), as he says ``purely physical definition of meaningful information.'' Ontological information, in the sense used in this paper, exists whether there is any correlation or not; it is the form of nature in a specific sense; nature as such has no meaning. Rovelli's concept of information seems to be just another mathematical representation of a certain perspective on nature's organization with rather overextended concept of meaning. The seat of meaning is a conscious agent, not physical structures, even if the ultimate nature of consciousness is biological.

@@

In a sense, both types of information exist, ontological as something concrete and epistemic as an abstract view of knowledge. From this perspective, ontological information acts as the carrier of what can potentially become epistemic information. Indeed, it is its main source, with the cognitive faculties of the mind itself being another source. I\textsubscript{e} is contingent, dependent, and relative because it is located in the mind. I\textsubscript{o}, meanwhile, is objective and meaningless, because it exists as a physical fact. We may need I\textsubscript{o} to get I\textsubscript{e}, but I\textsubscript{e} acquires its own ``persistence'' once created. While there is an obvious bottom-up causation from I\textsubscript{o} to I\textsubscript{e}, there is also a top-down causation from I\textsubscript{e }to I\textsubscript{o}. This means that in many cases, the forms and organization in physical reality (e.g., manmade objects) are expressions of mental concepts (I\textsubscript{e}). We may therefore imply an emergence relation between the two forms of information. However, this emergence must be properly understood. I\textsubscript{e} emerges from I\textsubscript{o} as a non-reducible ``entity.'' I\textsubscript{e} cannot be explained purely in terms of I\textsubscript{o}, because it acquires features that do not exist at the I\textsubscript{o} level. Another interpretation would involve regarding I\textsubscript{o }as representing the level of physical reality, which is in itself a multi-level reality with complex structures at different levels of organization for nature. In fact, we have multiple levels of I\textsubscript{o} to reflect nature's complexity. I\textsubscript{e}, meanwhile, represents the reality at the level of a living conscious agent. This reflects I\textsubscript{o}, but the agent creates its own specific representation. Which particular interpretation of I\textsubscript{o} and I\textsubscript{e} is most accurate should be the subject of future research.
